---
title: "Map"
author: "Ruijie Chang"
date: "2021/12/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(spatstat)
library(here)
library(sp)
library(rgeos)
library(maptools)
library(GISTools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)

##First, get the London Borough Boundaries
LondonBoroughs <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))

library(stringr)
BoroughMap <- LondonBoroughs %>%
  dplyr::filter(str_detect(GSS_CODE, "^E09"))%>%
  st_transform(., 27700)

```{r}
qtm(BoroughMap)
```



##Now get the location of all Blue Plaques in the City
BluePlaques <- st_read("https://s3.eu-west-2.amazonaws.com/openplaques/open-plaques-london-2018-04-08.geojson")

BluePlaques <- st_read(here::here(
                                  "open-plaques-london-2018-04-08.geojson")) %>%
  st_transform(.,27700)

summary(BluePlaques)

```{r}
#plot the blue plaques in the city
tmap_mode("plot")

tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaques) +
  tm_dots(col = "blue")

```

#remove duplicates
library(tidyverse)

library(sf)
BluePlaques <- distinct(BluePlaques)

BluePlaquesSub <- BluePlaques[BoroughMap,]
#check to see that they've been removed
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")
  
#extract the borough

Harrow <- BoroughMap %>%
  filter(., NAME=="Harrow")

#Check to see that the correct borough has been pulled out
tm_shape(Harrow) +
  tm_polygons(col = NA, alpha = 0.5)

#clip the data to our single borough
BluePlaquesSub <- BluePlaques[Harrow,]
#check that it's worked
tmap_mode("plot")

```{r}

tm_shape(Harrow) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")
```

#now set a window as the borough boundary
window <- as.owin(Harrow)
plot(window)

#create a sp object
BluePlaquesSub<- BluePlaquesSub %>%
  as(., 'Spatial')

```{r}
#create a ppp object
BluePlaquesSub.ppp <- ppp(x=BluePlaquesSub@coords[,1],
                          y=BluePlaquesSub@coords[,2],
                          window=window)
                          
BluePlaquesSub.ppp %>%
  plot(.,pch=16,cex=0.5, 
       main="Blue Plaques Harrow")
```
```{r}
       
BluePlaquesSub.ppp %>%
  density(., sigma=500) %>%
  plot()
```


#First plot the points
plot(BluePlaquesSub.ppp,
     pch=16,
     cex=0.5, 
     main="Blue Plaques in Harrow")

#now count the points in that fall in a 6 x 6
#grid overlaid across the windowBluePlaquesSub.ppp2<-BluePlaquesSub.ppp %>%
BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6)%>%
    plot(., add=T, col="red")

#run the quadrat count
Qcount <- BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame() %>%
  dplyr::count(Var1=Freq)%>%
  dplyr::rename(Freqquadratcount=n)  

Qcount %>% 
  summarise_all(class)

sums <- Qcount %>%
  #calculate the total blue plaques (Var * Freq)
  mutate(total = Var1 * Freqquadratcount) %>%
  dplyr::summarise(across(everything(), sum))%>%
  dplyr::select(-Var1) 

lambda<- Qcount%>%
  #calculate lambda
  mutate(total = Var1 * Freqquadratcount)%>%
  dplyr::summarise(across(everything(), sum)) %>%
  mutate(lambda=total/Freqquadratcount) %>%
  dplyr::select(lambda)%>%
  pull(lambda)
```{r}
QCountTable <- Qcount %>%
  mutate(Pr=((lambda^Var1)*exp(-lambda))/factorial(Var1))%>%
  #now calculate the expected counts based on our total number of plaques
  #and save them to the table
  mutate(Expected= (round(Pr * sums$Freqquadratcount, 0)))

#Compare the frequency distributions of the observed and expected point patterns
plot(c(1,5),c(0,14), type="n",
xlab="Number of Blue Plaques (Red=Observed,Blue=Expected)", 
     ylab="Frequency of Occurances")
points(QCountTable$Freqquadratcount, 
       col="Red", 
       type="o", 
       lwd=3)
points(QCountTable$Expected, col="Blue", 
       type="o", 
       lwd=3)
```
  
  